\documentclass[../proposal.tex]{subfiles}
\begin{document}

\section{Milestones}
In accordance with the bi-weekly schedule specified in the project requirements, we have constructed a series of milestones, interleaved with the actual project deadlines, that will allow us to consistently produce the necessary amount of work and remain on track to complete.

The first deadline has already passed, the initial project proposal.

The first milestone is the initial implementation of the OpenAI Gym environment, along with the creation of the Project Report structure and completion of the Introduction section.

The second deadline is the Environment Demo, in which we will be presenting the completed Gym environment with action and state spaces, reward structure, and step functions implemented.

The second milestone is the selection of algorithms for the Result Demo, as well as their preliminary implementation in the Gym environment. Additionally, we plan to complete the Project Report's Approaches section.

The third milestone is the experimentation and data collection after running RL agents with various algorithms, along with the completion of the Empirical Studies section of the Project Report.

The third deadline is the Result Demo, in which we will present our analysis of the results of our experiments, and how our implementation was able to solve the problem. We also aim to have the Project Report's Conclusion section done by this point.

The fourth and final deadline is for the Project Report, which at this point should be finished, with earlier milestones having taken care of each section.
\label{milestones}

%note: this table will be at the top of the page that it is on always, so when on the first page it would go before the title.
\begin{table}
    \caption{Milestone Dates}
    \label{dates-table}
    \centering
    \begin{tabular}{lll}
        \toprule
        \multicolumn{2}{c}{Part}                                                              \\
        \cmidrule(r){1-2}
        Date     & Milestone                                                                  \\
        \midrule
        01/10/2023 & Project Proposal                                                         \\
        30/10/2023 & Milestone 1 (Gym Implementation and Report - Introduction)               \\
        30/10/2023 & Enviroment Demo                                                          \\
        30/10/2023 & Milestone 2 (Algorithm Selection and Report - Approaches)                \\
        30/10/2023 & Milestone 3 (Data Collection and Report - Empirical Studies)             \\
        06/12/2023 & Result Demo                                                              \\
        10/12/2023 & Project Report                                                           \\
        \bottomrule
    \end{tabular}
\end{table}
  
\end{document}